Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-31 paper/paper.tex
more TODO VL's
address ja's comment

Considering an output of the system, that is a features vector $F_n$ per sound $s_n$, the precision at rank $5$ is computed for each of the $D_k$ clusterings, and the $31$ p@5 are averaged to obtain the ap@5.

For a given reference clustering $D_k$, the p@5 is computed as follows.
For each sound $s_q, 0<q\leq9346$ considered as a query, its 5 nearest neighbors $s_n, 0<n\leq5$ in the timbre space under evaluation are retrieved using the Euclidean distance between corresponding features vectors.
For this query, the precision is defined as:
$$
p@5_q = \frac{1}{5} \sum_{n=1}^5 \mathbf{1}_{D_q=D_n}
$$
The p@5 is the average $p@5_q$ computed over all queries.
\ja{This is perhaps better described in reverse, starting with $p@5_q$, then $p@5$, then $ap@5$?
Also, we define the precisions here as proportions (between zero and one), but later, we present them as percentages (between $0\%$ and $100\%$).}%

@@

The processing pipeline is composed of two main building blocks.
The first block $B_1$ takes a digital audio recording as input and outputs one vector of features.
For this block, the main factors are the time support $B_1^t$ for computing the features and the type of features $B_1^f$.
We considered $B_1^t \in \{ 25, 128, 250, 500, 1000 \}$ ms and $B_1^f \in \{ \text{MFCCs}, \text{separable scattering}, \text{joint scattering} \}$.
The MFCCs are the standard mel-frequency cepstral coefficients with $40$ coefficients out of which we select the first $13$.
\ja{I'm not sure I like this notation.
First, why do we need to label the blocks ($B_1$ and $B_2$)?
We only have two of them.
Isn't it more straightforward to just call them ``the unsupervised part'' and ``the learned part'' or something like that?
We can also replace $B_1^t$ with something more straightforward, like $T$ (otherwise, it's a lot of bits to encode very little information).
Likewise, instead of $B_1^f$, we can just have $F$.}

@@

The complete experiments with all settings have been computed.
For the sake of clarity, only part of the results are discussed here.
\ja{What does this mean?}%

The best performing system considers the separable scattering computed over $1000~\mathrm{ms}$ time support, projected using the LMNN algorithm.
\ja{Separable scattering?
Not the joint?}%
Evaluated over the entire dataset, that is the computation of the projection and the evaluation are performed on the whole dataset, this system reaches the satifactory performance of $99.5\%$ of $ap@5$.
That means that, for a given sound dataset of \ipts for which subjective evaluation of similarity between \ipts are available, a very large number of queries would return interesting results to the user using this processing pipeline.
\ja{What conclusion do we draw from this?}

>>>>

% TODO VL: move the following paragraph down so that we explain: (1) p@5_q, (2) p@5, (3) ap@5.
Considering an output of the system, that is a features vector $F_n$ per sound $s_n$, the precision at rank $5$ is computed for each of the $D_k$ clusterings, and the $31$ p@5 are averaged to obtain the ap@5.

For a given reference clustering $D_k$, the p@5 is computed as follows.
For each sound $s_q, 0<q\leq9346$ considered as a query, its 5 nearest neighbors $s_n, 0<n\leq5$ in the timbre space under evaluation are retrieved using the Euclidean distance between corresponding features vectors.
For this query, the precision is defined as:
$$
p@5_q = \frac{1}{5} \sum_{n=1}^5 \mathbf{1}_{D_q=D_n}
$$
The p@5 is the average $p@5_q$ computed over all queries.
\ja{This is perhaps better described in reverse, starting with $p@5_q$, then $p@5$, then $ap@5$?
Also, we define the precisions here as proportions (between zero and one), but later, we present them as percentages (between $0\%$ and $100\%$).}%
% TODO VL: state that the AP@5 will be reported under the form of percentages throughout the rest of the paper.

@@

% TODO VL: make a block diagram.
The processing pipeline is composed of two main building blocks.
The first block $B_1$ takes a digital audio recording as input and outputs one vector of features.
For this block, the main factors are the time support $B_1^t$ for computing the features and the type of features $B_1^f$.
We considered $B_1^t \in \{ 25, 128, 250, 500, 1000 \}$ ms and $B_1^f \in \{ \text{MFCCs}, \text{separable scattering}, \text{joint scattering} \}$.
The MFCCs are the standard mel-frequency cepstral coefficients with $40$ coefficients out of which we select the first $13$.
\ja{I'm not sure I like this notation.
First, why do we need to label the blocks ($B_1$ and $B_2$)?
We only have two of them.
Isn't it more straightforward to just call them ``the unsupervised part'' and ``the learned part'' or something like that?
We can also replace $B_1^t$ with something more straightforward, like $T$ (otherwise, it's a lot of bits to encode very little information).
Likewise, instead of $B_1^f$, we can just have $F$.}

@@

% TODO VL: turn into active present voice.
% We have an exhaustive benchmark on the Cartesian product of all design choices, but we report results under the form of an ablation study for the sake of conciseness.
The complete experiments with all settings have been computed.
For the sake of clarity, only part of the results are discussed here.
\ja{What does this mean?}%

The best performing system considers the joint time--frequency scattering computed over $1000~\mathrm{ms}$ time support, projected using the LMNN algorithm.
Evaluated over the entire dataset, that is the computation of the projection and the evaluation are performed on the whole dataset, this system reaches the satifactory performance of $99.5\%$ of $ap@5$.
That means that, for a given sound dataset of \ipts for which subjective evaluation of similarity between \ipts are available, a very large number of queries would return interesting results to the user using this processing pipeline.
\ja{What conclusion do we draw from this?}
% TODO VL: draw a big-picture conclusion from this wrt the original motivation of the paper.
